Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-07-03 pkg/circtree/inst/wind_paper/draft/draft.Rnw
Update ref tease paper
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3024 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 47fc84bf7ba5483a3dfd947b1cb6fd5794ebcc0f
Mini-adaption in the computational details
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3039 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 8e103c565f91bed9d689ce4f3456b6c820760968

    \citet{Lang+Lerch+Mayr:2019}.

@@

    data \citep{Lang+Lerch+Mayr:2019}.

@@

The computation time on a standard computer is in the order of 10\,milliseconds
for the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency and linear models must be
re-estimated for each time of interest, and independent climatological models
have to be fitted for all times of interest within a single calendar year,
whereas for all times of interest only a single circular tree and a single
circular forest model is required.

>>>>

    \citet{Lang+Lerch+Mayr:2020}.

@@

    data \citep{Lang+Lerch+Mayr:2020}.

@@

The computation time on a standard computer is in the order of milliseconds for
the circular fit (used for the persistency and the climatological model),
seconds for the estimation of the linear model and the circular tree, and from
a few minutes up to an hour for the estimation of the circular forest; the
latter strongly depends on the number of covariates employed and, hence, varies
between the two locations included in the application. However, for a single
station and forecast step, the persistency model must be re-estimated for each
time of interest, independent climatological and linear models have to be
fitted for all times of interest within a single calendar year, whereas for all
times of interest only a single circular tree and a single circular forest
model is required.
